Stable Hot Spot Analysis (Draft)

### 2017-06-17 paper-main.tex
updated introduction

But, similar to a cluster analysis, there does exist a high dependency of the identified hotspots on the detection method and in particular the parametrization of this method. The identified areas as well as their shape can vary highly. This volatility can lead to a decrease in trust in the result or in suboptimal allocations of scarce resources. Therefore it is necessary to measure and evaluate the stability of a hotspot analysis as well as the different parametrizations. 
In our initial work~\cite{SoH-GI-Forum}, we introduced a method to measure the stability of hotspots, the \emph{stability of hotspots} metric (SoH) and showed its use on the basis of temperature data .   
Here, we build upon that work and examine in more detail the impact of the 
different instantiations of the most typical parameter. We use the well known 
Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of 
this statistic, the Focal $G^*$~\cite{SoH-GI-Forum}. Those parameter are the 
size of the study area (focal matrix), the detail of the resolution 
(aggregation level) and the size of the neighbourhood (weight matrix). By 
varying over these parameter, we can compare the stability for all possible 
combinations and isolate the effect of single parameter by aggregation over the 
other parameter. 
We evaluate on the well-known taxi data set to show the applicability on real world use cases as well as to enable a simple replication.

>>>>

But, similar to a cluster analysis, the identified hotspots highly depend on 
the parametrization of the detection method. The identified areas as well as 
their shape can vary highly. This volatility can lead to a decrease in trust in 
the result or in suboptimal allocations of scarce resources. Therefore, it is 
necessary to measure and evaluate the stability of a hotspot analysis as well 
as the different parametrizations.

In our initial work~\cite{SoH-GI-Forum}, we introduced a method to measure the 
stability of hotspots, the \emph{stability of hotspots} metric (SoH) and showed 
its use on the basis of temperature data.
Here, we build upon that work and examine the impact of the 
different instantiations of the most typical parameters in more detail. We use 
the well known 
Getis-Ord statistic \cite{Ord.1995}, the standard $G^*$, and a modification of 
this statistic, the Focal~$G^*$~\cite{SoH-GI-Forum}.
Those parameters examined are
\begin{inparaenum}[(1)]
   \item size of the study area given as a focal matrix,
   \item pixel resolution i.e. aggregation level and 
   \item the size of the neighbourhood given as a weight matrix.
\end{inparaenum}
By varying over these parameter, we can compare the stability for all possible 
combinations and isolate the effect of a single parameter.
We evaluate the metrics on the well-known dataset of New York Taxi drives to 
show the applicability to real world use cases as well as to foster 
reproducibility.
